### 2020-12-10 README.Rmd
working on adding alternativeHS.

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# In the meantime it is easier to use the included data file "zone".
data(zone)
# Of course, usually one would use data files, control.csv and a zone.csv, which is 
# listed as the datafile within the control.csv. 
# zone <- makeequilzone(resdir,"control2.csv") # normally would read in a file
    equiltime <- (Sys.time())   # let's change the initial depletion
    origdepl <-  c(0.30,0.31,0.29,0.32,0.30,0.31,0.29,0.32) 
zoneDD <- depleteSAU(zone$zoneC,zone$zoneD,zone$glb,origdepl,zone$product,len=12)
out <- prepareprojection(zone$zone1,zone$zoneC,zone$glb,zoneDD,zone$ctrl)
  zoneDR <- out$zoneDP
  projC <- out$projC
  zoneCP <- out$zoneC
  midtime <- (Sys.time())

@@

  midtime <- (Sys.time())
mseproj <- applymcda(zoneCP,zoneDR,glb,ctrl,projC$projyrs,projC$inityrs)
sauzoneDP <- asSAU(mseproj,sauindex,saunames,B0,exB0)
  endtime <- (Sys.time())
  print(endtime - midtime)
# Now plot some results
  plotC <- function(nsau,saunames,reps,projyrs,plts=c(4,2)) {
    return(list(nsau=nsau,saunames=saunames,reps=reps,projyrs=projyrs,plts=plts))
  }

>>>>

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the resdir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_code/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_code/"
}
resdir <- paste0(ddir,"aMSEUse/conddata/generic")  # data and results directory
dirExists(resdir,make=TRUE,verbose=TRUE)
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# In the meantime it is easier to use the included data file "zone".
data(zone)
# Of course, usually one would use data files, control.csv and a zone.csv, which is 
# listed as the datafile within the control.csv. These must be stored in resdir
# zone <- makeequilzone(resdir,"control2.csv") # normally would read in a file
    equiltime <- (Sys.time())   # let's change the initial depletion
    origdepl <-  c(0.30,0.31,0.29,0.32,0.30,0.31,0.29,0.32) 
zoneDD <- depleteSAU(zone$zoneC,zone$zoneD,zone$glb,origdepl,zone$product,len=12)
out <- prepareprojection(zone$zone1,zone$zoneC,zone$glb,zoneDD,zone$ctrl)
  zoneDR <- out$zoneDP
  projC <- out$projC
  zoneCP <- out$zoneC
  midtime <- (Sys.time())

@@

  midtime <- (Sys.time())
  applyHS <- mcdahcr   # name the HS/HCR to be used
mseproj <- doprojection(zoneCP,zoneDR,glb,ctrl,projC$projyrs,projC$inityrs)
sauzoneDP <- asSAU(mseproj,sauindex,saunames,B0,exB0)
  endtime <- (Sys.time())
  print(endtime - midtime)
# Now plot some results
  plotC <- function(nsau,saunames,reps,projyrs,plts=c(4,2)) {
    return(list(nsau=nsau,saunames=saunames,reps=reps,projyrs=projyrs,plts=plts))
  }
